ZCB Pricing

### 2018-08-02 ZCB Pricing .Rmd
More convergence

par(mfrow = c(2,2))
plot(1:8,senses[1,2:9])
lines(1:8,senses[2, 2:9], col="red", type="l")

@@

```{r 13}
# Convergence Tests
# Varying time steps

@@

plot(closed, x = time_vec, type = "l", ylim = c(0.53,0.65), xlab = "Number of time steps", ylab = "Estimated Price")
lines(x = time_vec, y = CN_conv, type = "l", lty = 2)
lines(x = time_vec, y = Impl_conv, type = "l", lty = 3, col = "blue")
lines(x = time_vec, y = Expl_conv, type = "l", lty = 4, col = "red")
legend(x = 60, y = 0.6, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = 1:4, col = c("black","black","blue", "red"), cex = 0.8)

@@

>>>>

#par(mfrow = c(2,2))
#plot(1:8,senses[1,2:9])
#lines(1:8,senses[2, 2:9], col="red", type="l")

@@

```{r 13}
# Convergence Tests for finite difference methods
# Varying time steps

@@

par(mfrow = c(1,1))
plot(closed, x = time_vec, type = "l", ylim = c(0.53,0.65), xlab = "Number of time steps", ylab = "Estimated Price")
lines(x = time_vec, y = CN_conv, type = "l", lty = 2)
lines(x = time_vec, y = Impl_conv, type = "l", lty = 3, col = "blue")
lines(x = time_vec, y = Expl_conv, type = "l", lty = 4, col = "red")
legend(x = 60, y = 0.6, legend = c("Closed Form", "Crank-Nicolson", "Implicit", "Explicit"), lty = 1:4, col = c("black","black","blue", "red"), cex = 0.8)

@@

```{r}
# Covergence tests for Monte Carlo functions

trials_vec <- seq(10,2000,50)

closed_1 <- NULL
CR_conv <- NULL
AV_conv <- NULL
MM_conv <- NULL
CV_conv <- NULL

for (i in 1:length(trials_vec)){
  closed_1[i] <- bond_price()
}

for (i in 1:length(trials_vec)){
  CR_conv[i] <- Crude_Monte_Carlo(n = trials_vec[i])
}

for (i in 1:length(trials_vec)){
  AV_conv[i] <- Antithetic_variates(n = trials_vec[i])
}

for (i in 1:length(trials_vec)){
  MM_conv[i] <- Moment_Matching(n = trials_vec[i])
}

for (i in 1:length(trials_vec)){
  CV_conv[i] <- Control_Variates_estimate(n = trials_vec[i])
}

plot(closed_1, x = trials_vec, type = "l",ylim = c(0.61,0.63), xlab = "Number of Trials", ylab = "Estimated Price")
lines(x = trials_vec, y = CR_conv, type = "l", lty = 2)
lines(x = trials_vec, y = AV_conv, type = "l", lty = 3, col = "blue")
lines(x = trials_vec, y = MM_conv, type = "l", lty = 4, col = "red")
lines(x = trials_vec, y = CV_conv, type = "l", lty = 5, col = "grey")

legend(x = 1500, y = 0.618, legend = c("Closed Form", "Crude", "Antithetic Variates", "Moment Matching","Control Variates"), lty = 1:5, col = c("black","black","blue", "red","grey"), cex = 0.5)
